Adaptive Video Streaming with Optimized Bitstream Extraction and PID-based Quality Control

### 2015-07-16 tmm.tex
add the corresponding author note

% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
\author{Shengbin~Meng,~Jun~Sun,~Yizhou~Duan~and~Zongming~Guo,~\em{Member,~IEEE} % <-this % stops a space
\thanks{Manuscript received July 15, 2015.}
\thanks{The authors are with the Institute of Computer Science and Technology, Peking University, Beijing%
, 100080, China (e-mail: shengbin@pku.edu.cn; sunjun@pku.edu.cn; duanyizhou@pku.edu.cn; guozongming@pku.edu.cn).}}

@@

In (\ref{eq:long-actual}) and (\ref{eq:long-check}), $T_l$ stands for the last quality change time. Theoretically, the integral part should be recorded and calculated since the system start. In practice, however, bandwidth may vary significantly during the transmission. If the integral part was recorded for too long time, it may not reflect the real network status and may slow down the reaction for better quality level. A compromise here is to choose a relatively long time, i.e., the time from last quality change till now, for the integral part calculation.

>>>>

% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
\author{Shengbin~Meng,~Jun~Sun,~Yizhou~Duan~and~Zongming~Guo,~\em{Member,~IEEE} % <-this % stops a space
\thanks{Manuscript received July 15, 2015.}
\thanks{The authors are with the Institute of Computer Science and Technology, Peking University, Beijing%
, 100080, China (Email: shengbin@pku.edu.cn, sunjun@pku.edu.cn, duanyizhou@pku.edu.cn, guozongming@pku.edu.cn; Phone: +86 1082529615; Fax: +86 1082529207). Jun Sun is the corresponding author.}}

@@

In (\ref{eq:long-actual}) and (\ref{eq:long-check}), $T_l$ stands for the last quality change time. Theoretically, the integral part should be recorded and calculated since the system starts. In practice, however, bandwidth may vary significantly during the transmission. If the integral part was recorded for too long time, it may not reflect the real network status and may slow down the reaction for better quality level. A compromise here is to choose a relatively long time, i.e., the time from last quality change till now, for the integral part calculation.
